Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and at administrative complexities.

@@

Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

>>>>

Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and also at administrative complexities.

@@

Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not"  ??????? Robin M. Hogarth and Natalia Karelaia 2011 Entrepreneurial success and failure MAIN BIB ?????????. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
